\section{Results}
\subsection{Resistor Phantom - System Characterisation}
For resistor phantom measurements, the average signal amplitude across 363 measurement combinations and 4235 repeats was 2.66 mV $\pm$ .24 mV standard deviation. The mean noise value for 100 repeats was 0.356 $\mu$V $\pm$ .058 $\mu$V St. Dev., equivalent to 77.5 dB $\pm$ 1.3 dB SNR. As has been found with other EIT systems \cite{oh2007multi}, the long term noise increased, with 0.637 $\mu$V $\pm$ .064 $\mu$V or 72.4 dB $\pm$ 0.66 dB for one hour and 1.522 $\mu$V $\pm$ .205 $\mu$V or 64.9 dB $\pm$ 1.24 dB and four hour recordings. As the short term SNR was unchanged throughout the recording when considering consecutive blocks of 100 measurements figure \ref{SNR}, this decrease in SNR 
%[this is interpretation which shouldnt be in results - ? correlated with] 
long term drifts from the baseline voltage. Over the course of the four hour recording, the mean change in voltage was 5.61 $\mu$V $\pm$ 1.04 $\mu$V or 0.21 \% $\pm$ 0.04 \%. 
%[again this is interpretation and shouldnt be in results - if you have measured data on these put here otherwise needs to go under discussion]. 
These arise predominantly from temperature changes within the current source, and variations in power supply voltage.

The reciprocity error was 0.42 \%. 



\subsection{Resistor Phantom - Frequency response}
[this is slightly confusing. WHy not start with the filter characteristics then introduce the measurements saying match filter charactetistic to within ... \%] The mean amplitude decrease, figure \ref{freqresp}, was 1.86 mV V or 21.0\%  from 20 Hz to 2 kHz for the BioSemi and 0.57 mV or 6.26\% for the actiCHamp across the same range. Across the full 20 kHz range the total decrease was 9.15 mV or  99.6 \%.  In both cases these frequency responses matched those of the anti-aliasing filter within the EEG systems, with cut-offs (-3dB) at 1.7 kHz and 7.5 kHz for the BioSemi and ActiCHamp respectively. Below these cut off frequencies, there was no significant change in mean SNR across frequency, ranging from 66 to 72 dB for the BioSemi and 69 and 75 dB for the ActiChamp.  