\subsection{Experimental Design}

Experiments were initially carried out on a resistor phantom to characterise the system across a range of frequencies. Subsequently, the system was utilised in all four EIT applications previously described, and the performance evaluated in each case. In some instances, the data were collected as part of other studies, Where the main aim was successfully imaging the impedance change of interest. In these cases additional analysis of the data was required to extract the relevant performance characteristics.

For the initial resistor phantom measurements, direct comparisons with systems reported in the literature are difficult to perform as the exact testing conditions and analyses are not always explicitly stated, e.g. load used, which measurements were included and how many repetitions were used in calculations. Therefore, we have chosen to use phantoms and measurement paradigms which represent realistic usage in brain EIT applications. Specifically, the injected current amplitudes complied with IEC 60601-1 \cite{IEC} safety limits, the number of measurements and the averaging time was chosen to match those used to collect data for real EIT reconstructions. Results are presented as a mean and standard deviation across all voltage measurements, with the exception of those with a standing potential below a threshold based on the results from \citet{packham2012comparison}, which are routinely neglected during reconstruction. After processing, for each experiment, c. 300 - 800 voltage measurements were included in further analysis. Thus the results represent the realistic best case performance of the system in a animal or human experiment, as opposed to the maximum achievable on a test bench. The first experiment investigated the noise and drift in measurements over time by replicating the use of the system in a long term monitoring application using at a single measurement frequency. The reciprocity error (RE), a common metric for evaluating the accuracy of EIT systems, was also calculated, where the ratio of the impedance measured with the voltage and current electrode pairs swapped, in a four terminal measurement. Ideally, these two measures are identical, in reality errors $<$ 0.5 \% are achieved in state-of-the-art EIT systems \cite{Hun_Wi_2014}. 

With a purely resistive test object, the amplitude of the measured voltages should be frequency independent. In reality, the components any system will exhibit some variations with frequency, necessitating some degree of calibration in post processing \cite{Hun_Wi_2014,McEwan_2006}. In the case of the ScouseTom system, the component with the greatest frequency dependence is the anti-aliasing filter within the EEG systems. To study the frequency dependence of the system as whole, changes in amplitude across frequency using two commercial EEG systems were compared to the theoretical changes resulting from their hardware filters. 

To assess the system when used in standard time difference mode, data was collected in healthy subjects using scalp EEG electrodes to represent the expected resting noise during scalp EIT recordings \cite{Fabrizi_2006,fabrizi2007analysis,Romsauerova2006}. Additionally, the suitability of the system for imaging impedance changes resulting from stroke in rats was assess from further analysis of data acquired during a feasibility study by \citet{Dowrick_2016}. The system was then utilised in measurements of evoked activity in the rat somatosensory cortex, using a methodology established using a system developed previously in the UCL group \cite{Oh2011,Aristovich_2016}. This enables a direct comparison of both data and resultant image quality with the system described in this study. Multi-frequency data were collected as part of a larger study in stroke patients in collaboration with University College London Hospital (UCLH). The noise performance of the system was evaluated across a range of frequencies used in a previous simulation study \cite{Malone2014a}, with a subset of frequencies recorded for longer period of time using the same paradigm as the healthy subjects in time difference mode. This data was used to investigate both the variations in performance of the system over the total frequency range, and also the degradation in data quality resulting from transferring from laboratory to clinical measurements. Finally, the system was used in the impedance sweep mode of operation in a study by \citet{Dowrick_2015}, characterising the impedance of healthy and ischaemic rat brain \emph{in vivo}. 

