\subsection{Experimental Data}


Each of the modes of operation previously described have been used in experimental settings. 

\subsubsection{Scalp electrode preparation}
blah
\subsubsection{Image Reconstruction}
blah





\subsubsection{Time difference}
\label{methodsTD}
'Standard' time difference EIT data was collected for imaging stroke in a rat model \cite{Dowrick_2016}. Using 100\( \mu \)A at 2kHz and c. 60 injection pairs, a frame of EIT data was recorded every minute, over 30 minutes. [another backwards sentence...Id redo as ; Recordings made in the anethetised rat... electrodes were, recording was......uL of hep blood were introduced into the at 10 min. This produced an impedance increase of... as the resistance of blood is .... (ref) comapred to that of brain (ref). Must always give sufficient standalone technical detail so reader cna grasp the measurement without the need to look up another paper.] A haemorrhage model where blood was injected into the brain over a 10 minute period, was triggered at the 10 minute mark, which was expected to cause a net impedance decrease. EIT images were produced using a 0th order Tikhonov algorithm on a 4 million element mesh of a generic rat skull [give ref and should introduce the image recon and stats used under exptl design section].

To assess the performance of the system in a clinically realistic scenario, recordings were made in 10 ?healthy subjects [need more details ? any neurological conditions excluded] at rest with 32 commercial EEG electrodes (EasyCap, Germany, www.easycap.de) configured using the standard EEG 10-20 \cite{Jasper1958} and 10-10 extension \cite{Oostenveld2001} systems. To apply electrodes, the skin was cleaned with alcohol and abraded before applying conductive paste [details ? Nu-prep and manuf details]. Current was injected at 1.2 kHz and 160 $\mu$ A, for 64 cycles or 54 ms, between 31 pairs of electrodes, for a total of 930 measurements for a complete frame. This protocol was repeated 60 times over the course of 20 minutes for each patient. In subsequent analysis, channels below 1 mV standing potential were considered, totalling 540. 

\subsubsection{Triggered}

The ScouseTom system was utilised in measurements of evoked activity in the rat somatosensory cortex, following electrical stimulation of the forepaw [need much more detail so clear on a standalone reading] \cite{Aristovich_2016} \cite{Vongerichten_2016}, with an increased number of electrodes, from 32 on a single hemisphere to 128 with 64 on each hemisphere [unclear state exactly how many electrodes and number of recordings with each. The stimuli delivered were 10 mA pulses 1 ms duration at a rate of 2 Hz, triggered by the ScouseTom controller.

Current was injected at 1.7 kHz with 50 $\mu$ A amplitude, for 30 seconds across a pair of electrodes, with voltages on 127 electrodes recorded in parallel using the ActiChamp ActiveTwo system with 25 kHz sampling rate. The voltages were demodulated with 1 kHz bandwidth, yielding 2 ms time resolution, and coherent averaging was performed on 60 500 ms trials centered around the time of stimulation. This process was repeated for c. 50 pairs of injection electrodes over the course of 25 minutes to produce a complete data set of c. 6000 voltages. EIT images were reconstructed at each 2ms time point in c. 80000 element hexahedral mesh, using the methodology outlined in \cite{Aristovich_2014}.




